DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-07-25 paper/paper.tex
add posterior for gamma
fix posterior
truth

@@

@@

@@

@@

\[\prod_{t=1}^T N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2) N(\eta, \xi^2)\]

\[\]

>>>>

\subsection{Supra-Bayesian Truth Estimation}

Imagine that you are a decision maker observing the network of media firms.  You wish to develop some estimate of "truth" for each news story you observe based on who is posting about the news story.  To do this you may approach the problem as a supra-Bayesian.  Consider that each agent in the network has some belief about the truth of a news event $p_i(T | \textbf{s})$ where $\textbf{s}$ is some signal about the world.  The supra-Bayesian would treat each agent's beliefs as data for his own beliefs

\[p(T | \bar{p}) \propto p(\bar{p} | T) p(T)\]

where $\bar{p} = \{p_1(T | \textbf{s}), ... p_N(T | \textbf{s})\}$.  If each agent's beliefs and signals were indepedent then this would be the same as

\[p(T | \bar{p}) \propto p(p_1 | T), .... p(p_N | T) p(T)\]

However, this is obviously not the case here as each agent can observe the signals of other agents and decide what to publish based on this.  So we need some way to control for the possible noise from other signals.  Ultimately, we want the probability of each agent holding their beliefs, given only their own signals.  If we have this then we can follow the above indepedent framework.

Let $p(p_i | T, \{s_j \forall j \in J\})$ be the probability of the $i$th agent holding their beliefs given a set of signals from the set of $J$ agents.  In this case $p(p_i | T, s_i)$ would be the probability of the $i$th agent holding their beliefs in the case where they receive no other signals.  This could also be written as $p(p_i | T, \!\{s_j \forall j \in J_{-i}\})$.  In the general case we can see that

\[p(p_i | T, \{s_j \forall j \in J\}) = \prod_{j=1}^J \gamma_{ij} p(p_i | T)\]

because $\gamma_{ij}$ is the trust that agent $i$ holds for $j$ and represents the probability that $i$ will use a signal from $j$.  Then we can see that

\[p(p_i | T, s_i) = p(p_i | T, \!\{s_j \forall j \in J_{-i}\}) = \prod_{j=1}^{J_{-i}} (1 - \gamma_{ij}) p(p_i | T)\]

Now consider the two agent case with the supra-Bayesian

\[p(T | \bar{p}) \propto (1 - \gamma_{12}) p(p_1 | T) (1 - \gamma_{21}) p(p_2 | T)  p(T)\]

This then provides a clear way to estimate the "truth" of a news story based on the dispersed beliefs of agents in a network.  NOTE: more on how to actually implement.

@@

\subsection{Supra-Bayesian Quality Estimation}

@@

NOTE: This section needs to be updated, the model is now completely different.

@@

\subsection{Posterior Specification for $\alpha_i$}

\[p(\alpha_i | \text{\boldmath$\alpha$}_{-i}, \gamma_i, \delta^2, \sigma^2, \chi) \propto p(\theta_i | \text{\boldmath$\alpha$}, \gamma_i, \delta^2) p(\alpha_i | \chi, \sigma^2)\]

\[= \prod_{t=1}^T N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2) N(\chi, \sigma^2)\]

\[\propto \exp\left\{-\frac{1}{2}\frac{(\text{\boldmath$\alpha$}^T \gamma_i)^T (\text{\boldmath$\alpha$}^T \gamma_i)}{\delta^2} + \frac{\sum_{t=1}^T (\text{\boldmath$\alpha$}^T \gamma_i)^T \theta_{it}}{\delta^2}\right\} \exp\left\{-\frac{1}{2}\frac{\alpha_i^T \alpha_i}{\sigma^2} + \frac{\alpha_i^T \chi}{\sigma^2}\right\}\]

\[\propto  \exp\left\{-\frac{1}{2}\frac{(\alpha_i \gamma_{ii})^T (\alpha_i^T \gamma_{ii})}{\delta^2} + \frac{\sum_{t=1}^T (\alpha_i^T \gamma_{ii})^T \theta_{it}}{\delta^2}\right\} \exp\left\{-\frac{1}{2}\frac{\alpha_i^T \alpha_i}{\sigma^2} + \frac{\alpha_i^T \chi}{\sigma^2}\right\}\]

\[\propto N(\mu_{\alpha i}, \Lambda_{\alpha i})\]

\[\Lambda_{\alpha i} = \left(\frac{I}{\sigma^2} + \frac{\gamma_{ii}^2}{\delta^2}\right)^{-1}\]

\[\mu_{\alpha i} = \Lambda_{\alpha i} \left(\frac{\chi}{\sigma^2} + \frac{T \gamma_{ii} \sum_{t=1}^T \theta_{it}}{\delta^2}\right)\]

@@

\[= \prod_{t=1}^T N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2) N(\eta, \xi^2)\]

\[\Lambda_{\gamma i} = \left(\frac{I}{\xi^2} + \frac{\text{\boldmath$\alpha$}\text{\boldmath$\alpha$}^T}{\delta^2}\right)^{-1}\]

\[\mu_{\gamma i} = \Lambda_{\gamma i} \left(\frac{\eta}{\xi^2} + \frac{T\text{\boldmath$\alpha$} \sum_{t=1}^T \theta_{it}}{\delta^2}\right)\]
